Can money buy happiness?

### 2022-04-29 finalproject.Rmd
File name change

Can money buy happiness? We sought to tell a story about the connection between economic prosperity and quality of life (most specifically happiness) while keeping in mind the added factor of working hours. We found that there is a loose inverse relationship between GDPPC and hours worked, which may highlight differences in technological processes between more and less developed countries. GDPPC does not serve as a perfect measure of the prosperity of a country’s people because it is skewed by income inequality and wealth distribution. GDPPC gives a near-sighted view of the standard of living in any given country, and it should not be used alone to measure something as qualitative as wellness (or happiness). Stressors and work hours are components that are not factored into GDPPC, and higher GDPPC does not even correlate with a greater amount of hours worked. This presents a paradox of sorts, it is commonly thought that more work generally means higher income, and higher income leads to more happiness. We can infer that less time spent working means increased leisure time which can be spent improving overall health and emotional well-being. We also can infer that a certain level of material well-being is necessary because it provides greater access to resources which in turn can boost happiness.  Economic prosperity and holistic well-being have a reciprocal relationship. Our research cannot possibly cover all factors such as access to community programs, optimal living conditions, or types of government and the length to which they go to provide resources. All of these ancillary factors play a role in happiness and the ability to work fewer hours, but we posit that looking purely at income and hours worked can still produce illuminating discoveries and ideas

>>>>

Can money buy happiness? We sought to tell a story about the connection between economic prosperity and quality of life (most specifically happiness) while keeping in mind the added factor of working hours. We found that there is a loose inverse relationship between GDPPC and hours worked, which may highlight differences in technological processes between more and less developed countries. GDPPC does not serve as a perfect measure of the prosperity of a country’s people because it is skewed by income inequality and wealth distribution. GDPPC gives a near-sighted view of the standard of living in any given country, and it should not be used alone to measure something as qualitative as wellness (or happiness). Stressors and work hours are components that are not factored into GDPPC, and higher GDPPC does not even correlate with a greater amount of hours worked. This presents a paradox of sorts, it is commonly thought that more work generally means higher income, and higher income leads to more happiness. We can infer that less time spent working means increased leisure time which can be spent improving overall health and emotional well-being. We also can infer that a certain level of material well-being is necessary because it provides greater access to resources which in turn can boost happiness.  Economic prosperity and holistic well-being have a reciprocal relationship. Our research cannot possibly cover all factors such as access to community programs, optimal living conditions, or types of government and the length to which they go to provide resources. All of these ancillary factors play a role in happiness and the ability to work fewer hours, but we posit that looking purely at income and hours worked can still produce illuminating discoveries and ideas.
